Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-06 paper/lostanlenRelevanceScattering.tex
cite mallat 2012 cpam

The wavelet scattering transform, described below, has both of these desired properties: invariance to time-shifting and stability to time-warping. The stability condition can be formulated as a Lipschitz continuity property, which guarantees that the feature transforms of $\boldsymbol{x}(t)$ and $\boldsymbol{x_\tau}(t)$ are close together if $|\tau'(t)|$ is bounded by a small constant.

>>>>

The wavelet scattering transform, described below, has both of these desired properties: invariance to time-shifting and stability to time-warping. The stability condition can be formulated as a Lipschitz continuity property, which guarantees that the feature transforms of $\boldsymbol{x}(t)$ and $\boldsymbol{x_\tau}(t)$ are close together if $|\tau'(t)|$ is bounded by a small constant \cite{mallat2012cpam}.
